Manuscript

### 2023-03-11 analysis/manuscript.qmd
Nicer button colors

  <a class="btn btn-primary btn-sm mb-1" href="/manuscript/output/manuscript.pdf" target="manuscript">
  <i class="fa-solid fa-file-pdf"></i>&ensp;PDF
  </a>

  <a class="btn btn-primary btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;PDF <small>(download)</small>
  </a>

  <a class="btn btn-info btn-sm mb-1" href="/manuscript/output-ms/manuscript-ms.pdf" target="manuscript">
  <i class="fa-solid fa-file-pdf"></i>&ensp;Manuscripty PDF
  </a>

  <a class="btn btn-info btn-sm mb-1" target="_blank" href="/manuscript/output-ms/manuscript-ms.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;Manuscripty PDF <small>(download)</small>
  </a>
</p>

>>>>

  <a class="btn btn-danger btn-sm mb-1" href="/manuscript/output/manuscript.pdf" target="manuscript">
  <i class="fa-solid fa-file-pdf"></i>&ensp;PDF
  </a>

  <a class="btn btn-danger btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;PDF <small>(download)</small>
  </a>

  <a class="btn btn-warning btn-sm mb-1" href="/manuscript/output-ms/manuscript-ms.pdf" target="manuscript">
  <i class="fa-solid fa-file-pdf"></i>&ensp;Manuscripty PDF
  </a>

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output-ms/manuscript-ms.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;Manuscripty PDF <small>(download)</small>
  </a>
</p>
